\bf Nonparametric Bootstrap KS Test with Stationary Time Series

### 2023-10-02 manuscript/manuscript.tex
Added Note to Manuscript

>>>>

Consider the goodness of fit statistic:
\begin{equation*}
KS_n := \sup_x|Y_n(x; \hat\theta)|, 
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{equation*}
where $F_n$ denotes the empirical distribution function based on $X_1,...,X_n$.
We note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x)),
\end{equation*}
where $F(x)$ is the true cdf (under the null $F(x) = F(x, \theta_0)$ for some
true parameter $\theta_0$).

Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^*_n$ the
empirical distribution of the bootstrap sample $X^*_1,...,X^*_n$ and let
$\hat\theta^*_n$ be the parameter estimate based on the bootstrap samples. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
\[
\sqrt{n}(F_n(x) - F(x))
\]
by that of
\[
\sqrt{n}(F^*_n(x) - F_n(x))
\]
and the distribution of
\[
\sqrt{n}(F(x; \hat\theta_n) - F(x))
\]
by that of
\[
\sqrt{n}(F(x; \hat\theta^*_n) - F(x; \hat\theta_n)).
\]
Therefore, if we define
\begin{equation*}
Y^*_n(x) = \sqrt{n}(F^*_n(x) - F_n(x)) - 
\sqrt{n}(F(x; \hat\theta^*_n) - F(x; \hat\theta_n)) 
= \sqrt{n}(F^*_n(x) - F(x; \hat\theta^*_n)) - 
\sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{equation*}
then $KS^*_n := \sup_x|Y^*_n(x)|$ is the bootstrap statistic that is expected
to approximate the distribution of $KS_n$. We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
Babu and Rao (2004).

We now consider the case where $X_i$'s are realizations from a time series and
$X^*_1,...,X^*_n$ are generated by block bootstrap. In this case, we can 
approximate the distribution of
\[
\sqrt{n}(F_n(x) - F(x))
\]
by that of
\[
\sqrt{n}(F^*_n(x) - E^*[F^*_n(x)])
\]
and the distribution of
\[
\sqrt{n}(F(x; \theta_n) - F(x))
\]
by that of
\[
\sqrt{n}(F(x; \hat\theta^*_n) - F(x; E^*[\hat\theta^*_n])).
\]
Here $E^*$ denotes the expectation with respect to the bootstrap distribution
(i.e., the randomness due to the resampling using block botostrap) conditional
on the observations $X_1,...,X_n$. We can compute $E^*[F^*_n(x)]$ and 
$E^*[\hat\theta^*_n]$ numerically (they can also be computed analytically, 
depending on the types of block bootstrap we use). For example, let 
$X^*_{1,b},...,X^*_{n,b}$ be the $b$th block bootstrap sample for 
$1 \leq b \leq B$. One can compute $F^*_{n,b}$ and $\hat\theta^*_{n,b}$ based on
$X^*_{1,b},...,X^*_{n,b}$. Then
\begin{equation*}
E^*[F^*_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^*_{n, b}(x),
E^*[\hat\theta^*_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^*_{n,b}.
\end{equation*}
In this case, we can define
\begin{equation*}
Y^*_n(x) = \sqrt{n}(F^*_n(x) - E^*[F^*_n(x)]) - 
\sqrt{n}(F(x; \hat\theta^*_n) - F(x; E^*[\hat\theta^*_n)]) 
= \sqrt{n}(F^*_n(x) - F(x; \hat\theta^*_n)) - 
\sqrt{n}(E^*[F^*_n(x)] - F(x; E^*[\hat\theta^*_n])),
\end{equation*}
and $KS^*_n = \sup_x|Y^*_n(x)|$.
